Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-05-07 papers/intro_paper/intro_paper.tex
added comments for Section III

We additionally investigate the effects of erroneously assuming that
an underlying non-GR signal can be well-described by a GR one. We do
this by estimating the parameters of our non-GR signals using the GR
waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
resulting one- and two-dimensional posteriors are shown in the right
panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
GW150914-like (top) and GW190521-like (bottom) signals
respectively. For both signals, we find the 2D $\SEOB$ estimates are
markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
this impact on the estimation of the GR parameters $\bxigr$ by changing the
magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. This gives us 
confidence that the $\pSEOB$ model can accurately measure QNM 
properties without biasing measurements of inspiral quantities, like masses and spins.
To compute the samples of the final mass and spin in the last row, we start from the samples
of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b}),
and then invert them using the fitting formula in Ref.~\cite{Berti:2005ys}.
The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
three unique sets of values for $(M_f,\chi_f)$. These predicted values are correctly 
recovered by the $\pSEOB$ waveform (bottom-right plot in Fig.~\ref{fig:gr_ngr_comparison}),
leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$.

>>>>

We additionally investigate the effects of erroneously assuming that
an underlying non-GR signal can be well-described by a GR one. We do
this by estimating the parameters of our non-GR signals using the GR
waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
resulting one- and two-dimensional posteriors are shown in the right
panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
GW150914-like (top) and GW190521-like (bottom) signals
respectively. For both signals, we find the 2D $\SEOB$ estimates are
markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
this impact on the estimation of the GR parameters $\bxigr$ by changing the
magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. This gives us 
confidence that the $\pSEOB$ model can accurately measure QNM 
properties without biasing measurements of inspiral quantities, like masses and spins. 
\textcolor{blue}{As we increase the deviation, the remnant object rings down at a higher frequency and damping time. The resulting $\pSEOB$ signal is longer than the GR ($\SEOB$) prediction. When we try to fit the $\SEOB$ model to this signal (left column of Fig.~\ref{fig:gr_ngr_comparison}), the template tries to fit parameters appropriate for a longer signal, i.e., smaller masses and spins. Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.}
To compute the samples of the final mass and spin in the last row, we start from the samples
of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b}),
and then invert them using the fitting formula in Ref.~\cite{Berti:2005ys}.
The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
three unique sets of values for $(M_f,\chi_f)$. These predicted values are correctly 
recovered by the $\pSEOB$ waveform (bottom-right plot in Fig.~\ref{fig:gr_ngr_comparison}),
leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$.
